### 2023-01-17 doc/manuscript/translocation.qmd
Add text describing evolutionary rescue expectations

@@

We estimated survival of translocated frogs, recruitment of new frogs into the adult population, and population size using a Bayesian open-population Jolly-Seber mark-recapture model with known additions (i.e., translocated cohorts) to the population, as implemented by the mrmr package [@joseph2019] and using R Statistical Software [v4.4.4; \@rsoftware2022]. The model tracks the states of *M* individuals that comprise a superpopulation made up of real and pseudo-individuals [see @joseph2018 for details]. The possible states of individuals include "not recruited", "alive", and "dead". The possible observations of individuals include "detected" and "not detected". We assume that individuals that are in the "not recruited" or "dead" states are never detected (i.e., there are no mistakes in the individual PIT tag records). For all models, we used mrmr defaults for priors, number of chains (4), and warmup and post-warmup iterations (2000 for each). We evaluated convergence of the Markov chain Monte Carlo (MCMC) algorithm using trace plots and Gelman-Rubin statistics (Rhat). Code used to construct CMR datasets and fit models for each translocated population is available from a GitHub repository ([https://github.com/SNARL1/cmr-analysis](https://github.com/SNARL1/cmr-analysis.)).

@@

| **Parameter**                                                             | **Value**            | **Source**                                                         |
|:----------------------------|:------------------|:-----------------------|
| $\sigma_{L_1}$, Yearly survival probability of year 1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_2}$, Yearly survival probability of year 2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_3}$, Yearly survival probability of year 3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_1}$, Yearly survival probability of year 1 juveniles           | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year 2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from mark-recapture studies                              |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from mark-recapture studies                              |
| $p_{L_1}$, Probability of a year 1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge |
| $p_{L_2}$, Probability of a year 2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_{J_1}$, Probability of a year 1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                 |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                 |
| $\omega$, Probability of juvenile successfully recruiting to an adult     | Varies yearly        | Explored different values of this parameter                        |

>>>>

Describe expectations if frog populations are recovering due to evolutionary rescue.

-   Differences in allele frequencies between naive and recovering populations

-   Shared selective response across recovering populations

-   Changes in population growth rate extend beyond the natal environment

-   In populations established via translocation of frogs from recovering populations, Bd load is not an important predictor of post-translocation frog survival (in contrast to important relationship between Bd load and frog survival during Bd-caused epizootics)

-   Population viability: Any expectation here?

Then show how each result is consistent with those expectations.

@@

We estimated survival of translocated frogs, recruitment of new frogs into the adult population, and population size using a Bayesian open-population Jolly-Seber mark-recapture model with known additions (i.e., translocated cohorts) to the population, as implemented by the mrmr package [@joseph2019] and using R Statistical Software \[v4.4.4; \@rsoftware2022\]. The model tracks the states of *M* individuals that comprise a superpopulation made up of real and pseudo-individuals [see @joseph2018 for details]. The possible states of individuals include "not recruited", "alive", and "dead". The possible observations of individuals include "detected" and "not detected". We assume that individuals that are in the "not recruited" or "dead" states are never detected (i.e., there are no mistakes in the individual PIT tag records). For all models, we used mrmr defaults for priors, number of chains (4), and warmup and post-warmup iterations (2000 for each). We evaluated convergence of the Markov chain Monte Carlo (MCMC) algorithm using trace plots and Gelman-Rubin statistics (Rhat). Code used to construct CMR datasets and fit models for each translocated population is available from a GitHub repository ([https://github.com/SNARL1/cmr-analysis](https://github.com/SNARL1/cmr-analysis.)).

@@

| **Parameter**                                                             | **Value**            | **Source**                                                         |
|:----------------------------|:-----------------|:-------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year 1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_2}$, Yearly survival probability of year 2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_3}$, Yearly survival probability of year 3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_1}$, Yearly survival probability of year 1 juveniles           | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year 2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from mark-recapture studies                              |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from mark-recapture studies                              |
| $p_{L_1}$, Probability of a year 1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge |
| $p_{L_2}$, Probability of a year 2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_{J_1}$, Probability of a year 1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                 |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                 |
| $\omega$, Probability of juvenile successfully recruiting to an adult     | Varies yearly        | Explored different values of this parameter                        |
